Reproducible Research Peer Assessment 1
=========================================
First, we will read in the data set from the local computer for processing the data
which we will call "FitBit"
```{r FitBitdataframe}
setwd("/Users/lfree61/Desktop/Reproducible Research")
FitBit<- (data.frame(read.csv("activity.csv", na.strings= "NA")))
FitBit1<- subset(FitBit, complete.cases(FitBit))
FitBit1<- transform(FitBit1, interval= factor(interval))
```

Next we will find the total number of steps per day and create a histogram: 

```{r histFitBit}
DateofSteps<- split(FitBit1$steps, FitBit1$date)
StepsperDay<- sapply(DateofSteps, sum)

hist(StepsperDay, breaks=10)
dev.copy(png, file= "figures\\hist_StepsperDay.png")
dev.off()
```

Learn the mean and median number of setps taken each day: 
```{r meanFitBit}
mean(StepsperDay)
median(StepsperDay)
```

From this we learn the avg pattern of activity per day, using a time series plot: 
```{r plotFitBit1}
StepsperInterval <- split(FitBit1$steps, FitBit1$interval)
AvgStepsperInterval<- sapply(StepsperInterval, mean)
plot(AvgStepsperInterval ~ levels(FitBit1$interval), 
  type= "1",
  xlab= "5 minute intervals",
  ylab= "Average number of Steps")
dev.copy(png, file = "figures\\seriesplotAvgStepsperInterval.png")
dev.off()
```##Now, let's determine which 5-min interval contains the maximum number of steps: 
## Determining the 5-min interval with the max steps
```{r maxStepsperInterval}
levels(FitBit1$interval)[which.max(AvgStepsperInterval)]
```

How many missing values are in this data set?
```{r missing vals}
sum(!complete.cases(FitBit))

## Strategy-- input missing value by filling datetime's with mean for that interval over all days where "FitBit2" is the new data set with the filled data
```{r}
FitBit2<- FitBit
emptyvalues<-  FitBit2[!complete.cases(fillData), 3]
availableintervals<-  as.numeric(names(AvgStepsperInterval))
FitBit2[!complete.cases(FitBit2), 1] = 
    AvgStepsperInterval[match(emptyvalues, availableintervals)]
```
## Create Histogram of new data set and report mean/median for total steps/day
```{r histofFitBit2}
DateofSteps<- split(FitBit2$steps, FitBit2$date)
StepsperDay<- sapply(DateofSteps, sum)
hist(StepsperDay, breaks=10)
dev.copy(png, file="figures\\histFitBit2.png")
dev.off()

## Report mean and median of Steps per day
mean(StepsperDay)
median(StepsperDay)

##Answer--As the missing values were no longer excluded, but instead filled with the new data values, the resulting values were different from FitBit2 from the first part of the assignment. 
```

What are the differences in activity patterns between weekdays and weekends?
```{r}
alldayswalked <- weekdays(as.Data(FitBit2$date))
weekeends<- (alldayswalked== "Saturday") | (alldayswalked == "Sunday")
alldayswalked[weekends] = "weekend"
alldayswalked[!weekends]= "weekday"
alldayswalked<- factor(alldayswalked, levels c("weekday", "weekend"))

FitBit2$date = alldayswalked
weekend<- subset(FitBit2, FitBit2$date =="weekend")
weekday<- subset(FitBit2, FitBit2$date == "weekday")
Avgsforweekend<- sapply(split(weekend$steps, weekend$interval), mean)
Avgsforweekday<- sapply(split(weekday$steps, weekday$interval), mean)
```
Let's look at a time series plot for the averages across all weekdays/weekends. 
```{r plotavgsalldayswalked}
par(mfrow = c(2, 1))
plot(Avgsforweekend ~ levels(FitBit1$interval),
     type="1",
     main="Weekend",
     xlab= "Time per day (5 min intervals)",
     ylab= "Avg number of steps")
plot(Avgsforweekday ~ levels(FitBit1$interval), 
      type="1", 
      main="Weekday",
      xlab= "Time per day(5 min intervals)", 
      ylab= "Avg number of steps")
dev.copy(png, file= "figures\\seriesplotFitBit2.png")
dev.off()
```
